Lifting CDCL to Relational Domains

### 2016-10-17 contributions.tex
contribution

\paragraph{Contributions}
In this paper, we make the following contributions.
\begin{compactenum}
\item We present a novel program analysis technique that 
lifts the CDCL algorithm to relational numerical abstract domains.   
We have implemented our technique in 2LS verification tool.  To 
the best of our knowledge, this is the first instantiation of CDCL 
algorithm with relational abstract domains.

@@

\item  Experiments on a set of benchmarks drawn from the bitvector 
category in SV-COMP as well as numerical programs and a few 
control-intensive benchmarks from hardware domain show that 
the strict generalization of CDCL algorithm effectively combines 
the efficiency of abstract domains while being path-sensitive and 
bit-precise at the same time.  
\end{compactenum}

>>>>

\paragraph{Contributions}
In this paper, we make the following contributions.
\begin{compactenum}
\item We present a novel program analysis technique that 
lifts the CDCL algorithm to relational numerical abstract domains.   
We have implemented our technique in 2LS verification tool.  
\Omit{
To the best of our knowledge, this is the first instantiation of CDCL 
algorithm with relational abstract domains. 
}

@@

\item  Experiments indicate a \rmcmt{N}X reduction in the number of 
decisions, propagations, learning and backtracking iterations compared to a 
SAT solver while being more precise compared to an abstract interpreter.  
\Omit {
set of benchmarks drawn from the bitvector regression category in 
SV-COMP, bit-precise software models auto-generated from hardware 
circuits domain and some hand crafted example show that 
}
\end{compactenum}

### 2016-10-17 experiments.tex
contribution

\section{Experimental Results}
We have implemented the instantiation of ACDCL on relational domains 
in 2LS verification tool~\cite{2ls}.  The abstract domains used for 
our experiments are intervals, template polyhedra, octagons and equalities.  
We verified a total of 70 benchmarks in ANSI-C, which are derived from 
(a) bit-vector regression category in SV-COMP'16, (c) bit-precise and 
cycle accurate software models of hardware circuits automatically 
generated using v2c~\cite{mtk2016}, (c) controller code generated 
from Simulink (d) several hand-crafted benchmarks for equivalence 
checking and bounded loop analysis.  All benchmarks containing 
bounded loops are completely unrolled before analysis.  We compare 
our tool with a state-of-the-art bounded model checker CBMC and a 
commercial static analysis tool, Astr{\'e}e.  CBMC uses MiniSAT 
solver in the backend.  Astr{\'e}e was configured with interval 
domain, trace-partition domain, and relational domains.  All the 
bounded loops are completely unrolled in Astr{\'e}e.

\Omit {
To enable precise analysis using Astr{\'e}e, all our benchmarks are 
manually instrumented with partition directives which provides external 
hint to the tool to guide the trace partitioning heuristics.  Usually, 
such high-precision is not needed for static analysis, since it makes 
the analysis very expensive.  Without trace partitioning, the 
analysis using Astr{\'e}e shows high degree of imprecision. 
}
\paragraph {\em Observation of Analysis}

@@

>>>>

\section{Experimental Results}
We have implemented the instantiation of ACDCL on relational domains
in 2LS verification tool~\cite{2ls}.  We have used the abstract domains
provided by 2LS (intervals, octagons, polyhedra and equalities) for our
experiments. Although the performance of the abstract domain implementations 
in 2LS is not competitive with that of APRON~\cite{apron} library, but 
the domain implementation in 2LS can handle all C operators 
(including bitwise operations) out of the box and support precise
complementation of meet irreducibles, which are necessary for our algorithm.

We verified a total of 70 benchmarks in ANSI-C, which are derived from 
(a) bit-vector regression category in SV-COMP'16, (c) bit-precise and 
cycle accurate software models of hardware circuits automatically 
generated using v2c~\cite{mtk2016}, (c) controller code generated 
from Simulink (d) several hand-crafted benchmarks for equivalence 
checking and bounded loop analysis.  All benchmarks containing 
bounded loops are completely unrolled before analysis.  We compare 
our tool with a state-of-the-art SAT-based bounded model checker 
CBMC~\cite{cbmc} and a commercial static analysis tool, Astr{\'e}e.  
CBMC uses MiniSAT solver in the backend.  Astr{\'e}e was configured with 
default set of domains which includes interval, bit-field, congurence and 
relational domains.  Additionally, to enable precise analysis using 
Astr{\'e}e, we also used trace-partition domain.

\Omit {
To enable precise analysis using Astr{\'e}e, all our benchmarks are 
manually instrumented with partition directives which provides external 
hint to the tool to guide the trace partitioning heuristics.  Usually, 
such high-precision is not needed for static analysis, since it makes 
the analysis very expensive.  Without trace partitioning, the 
analysis using Astr{\'e}e shows high degree of imprecision. 
}
\paragraph {\em \textbf{Observation of Analysis}}

@@

%================  
\input{graphs}
%================
